---
title: "Soy-rye analysis: 2019 project"
author: "Uriel D. Menalled"
date: "7/1/2020"
output: github_document
editor_options: 
  chunk_output_type: console
---

The nlme models were done using the covariate scheme recommended by Pinheiro and Bates (2000). While this approach lead to slightly higher AIC and slightly different p-values than modeling by hand in nlme, parameters of the nls, nlme-by hand, and nlme-covariate models were the same. Furthermore, the nlme-covariate approach was the only method that could properly account for nested random effects. 

# Library
```{r package loading}
library(tidyverse)
library(lmerTest)
library(openxlsx)
library(emmeans)
library(vegan)
library(goeveg)
library(labdsv)
library(nls.multstart)
library(ggpubr)
library(corrplot)
library(nlme)
library(outliers)
library(multcomp)
library(here)
```

# Weather
```{r}
WeatherData<-read.xlsx(here("Data","WeatherData.xlsx"),sheet=1)
WeatherData$Site<-as.factor(WeatherData$Site)
WeatherData$Month<-factor(WeatherData$Month,
                             levels=c("Jan","Feb","Mar","Apr","May","Jun","Jul",
                                      "Aug","Sep","Oct","Nov","Dec"))
WeatherData$Year<-factor(WeatherData$Year, levels = c("2019", "15-year avg."))
WeatherData$Month2<-as.numeric(WeatherData$Month)
tapply(WeatherData[WeatherData$Month %in% c("May","Jun","Jul","Aug","Sep","Oct"),]$Temp_C,
      WeatherData[WeatherData$Month %in% c("May","Jun","Jul","Aug","Sep","Oct"),]$Site, summary)
tapply(WeatherData[WeatherData$Month %in% c("May","Jun","Jul","Aug","Sep","Oct"),]$PPT_cm,
      WeatherData[WeatherData$Month %in% c("May","Jun","Jul","Aug","Sep","Oct"),]$Site, summary)

WeatherData2<-pivot_longer(WeatherData,col=c(Temp_C,PPT_cm),names_to = "Variable",values_to = "val")
WeatherData2$Variable<-factor(WeatherData2$Variable,
                              levels = c("Temp_C","PPT_cm"),
                              labels = c("Mean temperature","Cumulative monthly precipitation"))

ggplot(WeatherData2[WeatherData2$Month %in% c("May","Jun","Jul","Aug","Sep","Oct"),],aes(x=Month2,y=val,color=Site,lty=Year))+
  geom_line()+
  labs(y=expression(atop(paste("Temperature (", degree,"C)"))),
       x="Month")+
  scale_y_continuous(sec.axis = sec_axis(~.*1, name = "Precipitation (cm)"))+
  scale_x_continuous(breaks = 1:12,
    labels = c("Jan","Feb","Mar","Apr","May","Jun","Jul",
               "Aug","Sep","Oct","Nov","Dec"))+
  theme_bw(base_size = 14)+
  theme(panel.grid.minor = element_blank(),
        plot.margin=unit(c(1,1,1,1), "cm"),
        axis.title.y.left = element_text(vjust=-6),
        axis.title.y.right = element_text(vjust=3))+
  facet_wrap(~Variable)
```


# Soybeans
```{r loading in soy biomoss}
BiomassData<-read.xlsx(here("Data","Soybean_Wt.xlsx"))
table(BiomassData$Plot,BiomassData$Site) #The missing observation was not repeated
BiomassData<-BiomassData[,-c(1)]

BiomassData<-BiomassData %>% 
  mutate(Seeding=ifelse(Site=="Aur" & 
                            Plot%in% c(1,9,14,17),300,
                          ifelse(Site=="Aur" & 
                                 Plot%in% c(2,6,13,19),225,
                                 ifelse(Site=="Aur" &
                                          Plot%in% c(4,8,12,20), 150,
                                        ifelse(Site=="Aur" &
                                                 Plot%in% c(5,7,15,18), 75,
                                               ifelse(Site=="Aur" &
                                                        Plot%in% c(3,10,11,16),0,
                    ifelse(Site=="Gen" & 
                             Plot%in% c(4,10,13,16),300,
                           ifelse(Site=="Gen" &
                                     Plot%in% c(1,8,14,17),225,
                                  ifelse(Site=="Gen" &
                                           Plot%in% c(3,7,15,19),150,
                                         ifelse(Site=="Gen" &
                                                  Plot%in% c(2,9,11,20),75,
                                                0)))))))))) %>%
  dplyr::select(Site,Block,Plot,Treatment,Seeding,everything()) 
BiomassData$Treatment<-dplyr::recode(BiomassData$Treatment,High="120",Low="60",None="0")
BiomassData<-dplyr::rename(BiomassData,Nitrogen=Treatment)
BiomassData<-dplyr::rename(BiomassData,SoyBiomass='dry_wt.(g)')

BiomassData[c("Site","Block","Seeding")] <- 
  lapply(BiomassData[c("Site","Block","Seeding")], factor)

BiomassData$Nitrogen<-as.factor(BiomassData$Nitrogen)
BiomassData$Nitrogen<-factor(BiomassData$Nitrogen,levels = c("0","60","120"))

BiomassData[BiomassData$Site=="Gen",]$Seeding<-
  dplyr::recode(BiomassData[BiomassData$Site=="Gen",]$Seeding,
                "150"="75", "75"="150","225"="300","300"="225","0"="0")
BiomassData$Seeding<-as.factor(BiomassData$Seeding)

ggplot(BiomassData[!BiomassData$Seeding==0,],aes(Seeding,SoyBiomass,fill=Nitrogen))+
  geom_bar(stat='summary',fun="mean",na.rm=TRUE,position = "dodge")+
  stat_summary(geom = "errorbar",fun.data = "mean_se",na.rm = TRUE,
               width=.1,position = position_dodge(.9))+
  ylab("Total soybean biomass (g/0.5m2)")+
  scale_fill_grey(start = 0.8, end = 0.4)+
  theme_bw(base_size = 14)+
  theme(legend.position = "none")+
  facet_wrap(~Site)

#Not incluing seeding rate zero

SoyBiomassMod<-lmer(SoyBiomass~Seeding*Nitrogen+(1|Site/Block),
     data = BiomassData[!BiomassData$Seeding==0,])

plot(SoyBiomassMod)
hist(resid(SoyBiomassMod))
anova(SoyBiomassMod)

#Aurora
  SoyBiomassModAur<-lmer(SoyBiomass~Seeding*Nitrogen+(1|Block),
       data = BiomassData[BiomassData$Site=="Aur"&!BiomassData$Seeding==0,])

  plot(SoyBiomassModAur)
  hist(resid(SoyBiomassModAur))
  anova(SoyBiomassModAur)

#Geneva
  SoyBiomassModGen<-lmer(SoyBiomass~Seeding*Nitrogen+(1|Block),
       data = BiomassData[BiomassData$Site=="Gen"&!BiomassData$Seeding==0,])

  plot(SoyBiomassModGen)
  hist(resid(SoyBiomassModGen))
  anova(SoyBiomassModGen)

BiomassData2<-BiomassData
BiomassData2$Seeding<-as.numeric(as.character(BiomassData$Seeding))
BiomassData2$Site<-dplyr::recode_factor(BiomassData2$Site,"Aur"="Aurora","Gen"="Geneva")
```

```{r Yeild setup}
YieldData<-read.xlsx(here("Data","SoyRye_CompleteYieldData.xlsx"))
unique(YieldData$Treatment)
YieldData<-YieldData %>% 
  mutate(Seeding=ifelse(Site=="Aur" & 
                            Plot%in% c(1,9,14,17),300,
                          ifelse(Site=="Aur" & 
                                 Plot%in% c(2,6,13,19),225,
                                 ifelse(Site=="Aur" &
                                          Plot%in% c(4,8,12,20), 150,
                                        ifelse(Site=="Aur" &
                                                 Plot%in% c(5,7,15,18), 75,
                                               ifelse(Site=="Aur" &
                                                        Plot%in% c(3,10,11,16),0,
                    ifelse(Site=="Gen" & 
                             Plot%in% c(4,10,13,16),300,
                           ifelse(Site=="Gen" &
                                     Plot%in% c(1,8,14,17),225,
                                  ifelse(Site=="Gen" &
                                           Plot%in% c(3,7,15,19),150,
                                         ifelse(Site=="Gen" &
                                                  Plot%in% c(2,9,11,20),75,
                                                0)))))))))) %>%
  dplyr::select(Site,Block,Plot,Treatment,Seeding,everything()) 
YieldData$Treatment<-dplyr::recode(YieldData$Treatment,High="120",Low="60",None="0")
YieldData<-dplyr::rename(YieldData,Nitrogen=Treatment)

#YieldData<-YieldData[-67,]

YieldData$Nitrogen<-as.factor(YieldData$Nitrogen)
YieldData$Nitrogen<-factor(YieldData$Nitrogen,levels = c("0","60","120"))

YieldData[YieldData$Site=="Gen",]$Seeding<-
  dplyr::recode(YieldData[YieldData$Site=="Gen",]$Seeding,
                "150"="75", "75"="150","225"="300","300"="225","0"="0")
YieldData$Seeding<-as.factor(YieldData$Seeding)

YieldData %>% 
  group_by(Site,Seeding) %>% 
  summarise(AvgTestWeight=mean(TestWeight_lbsBu,na.rm=T)) %>% 
  arrange(Site,Seeding)

YieldData2<-YieldData %>% 
  filter(!Seeding==0) %>% 
  mutate(AvgSeedWeight_g=SeedWeight_g/Seed_num)

YieldData2$Seeding<-factor(YieldData2$Seeding,
                           levels=c(0,75,150,225,300))
```
##Emergence
-Make sure yield is loaded first
-I have confirmed that the conversions to plants/ha are correct.
```{r Emergence setup and analysis}
EarlyCounts<-read.xlsx(here("Data","EarlyCounts.xlsx"))
EarlyCounts$Nitrogen<-dplyr::recode(EarlyCounts$Nitrogen,High="120",Mid="60",Low="0")

CountsV1<-EarlyCounts %>% 
  mutate(Soy_num=(43560/(30/12)*(Soy_num/3.28084)),
         Stage="V1")
CountsV1$Seeding<-as.factor(CountsV1$Seeding)
CountsV1[CountsV1$Site=="Gen",]$Seeding<-
  dplyr::recode(CountsV1[CountsV1$Site=="Gen",]$Seeding,
                "150"="75", "75"="150","225"="300","300"="225","0"="0")

#Don't forget to load Yield data above to get the correction for the R8 dataframe
CountsR8<-YieldData %>% 
  dplyr::select(Site, Block, Plot, Nitrogen, Seeding, Soy_num) %>% 
  mutate(Soy_num=(43560/(30/12)*(Soy_num/3.28084)),
         Stage="R8")

EmergenceData<-rbind(CountsV1,CountsR8)
EmergenceData$Stage<-factor(EmergenceData$Stage,levels = c("V1","R8"))
EmergenceData$Seeding<-factor(EmergenceData$Seeding,
                              levels = c(0,75,150,225,300))

EmergenceData_Long<-EmergenceData %>% 
  mutate_if(is.numeric, round,0) %>%
  mutate(ID=paste(Site,Block,Nitrogen,Seeding,sep = ".")) %>% 
  pivot_wider(names_from = Stage,
              values_from = Soy_num)

EmergenceData_Long %>% 
  group_by(Site,Seeding) %>% 
  do(tTestMod=t.test(.$V1,.$R8,alternative="two.sided")) %>% 
  summarise(p_value=tTestMod$p.value)

EmergenceData_Long %>% 
  group_by(Site,Seeding) %>%
  summarise(SoyNumV1=mean(V1,na.rm=T),SoyDevV1=sd(V1,na.rm=T),
            SoyNumR8=mean(R8,na.rm=T),SoyDevR8=sd(R8,na.rm=T),
            PctChange=((mean(R8,na.rm=T)-mean(V1,na.rm=T))/mean(V1,na.rm=T)*100)) %>% 
  mutate_if(is.numeric, round,0) %>% 
  mutate(SoyNumV1=paste(SoyNumV1,paste("(",SoyDevV1,")",sep="")),
         SoyNumR8=paste(SoyNumR8,paste("(",SoyDevR8,")",sep=""))) %>% 
  dplyr::select(-c(SoyDevV1,SoyDevR8))

EmergenceData[c("Site","Block","Seeding","Stage")] <- 
  lapply(EmergenceData[c("Site","Block","Seeding","Stage")], factor)
EmergenceData$Soy_num<-round(EmergenceData$Soy_num,0)

EmergenceDataTest<-EmergenceData
EmergenceDataTest$SeedingMetric<-
  dplyr::recode(EmergenceDataTest$Seeding,
                "0"="0","75"="185,300","150"="370,700","225"="556,000","300"="741,300")
EmergenceDataTest<-EmergenceDataTest %>% 
  mutate(Soy_num_metric=Soy_num*2.47)
EmergenceDataTest$Nitrogen<-as.factor(EmergenceDataTest$Nitrogen)

EmergenceDataTest2<-EmergenceDataTest[!EmergenceDataTest$Seeding==0,]
EmergenceDataTest2$Block<-as.numeric(as.character(EmergenceDataTest2$Block))
EmergenceDataTest2<-EmergenceDataTest2 %>% 
  mutate(Block=case_when(
    Site=="Gen" ~ Block+4,
    TRUE~Block))

EmTest2<-lmer(log(Soy_num_metric)~Site+SeedingMetric*Stage*Nitrogen+
               (1|Block/SeedingMetric),
             data = EmergenceDataTest2)

plot(EmTest2)
anova(EmTest2)
###
cld(emmeans(EmTest2, specs = ~SeedingMetric|Stage),
            sort=F,adjust="none",Letters="abcde")
pairs(emmeans(EmTest2, specs = ~Stage|SeedingMetric))
range(EmergenceDataTest[EmergenceDataTest$Stage=="V1",]$Soy_num_metric)

EmergenceDataTest2<-EmergenceDataTest
EmergenceDataTest2$SeedingMetric<-gsub(",","",EmergenceDataTest2$SeedingMetric)
EmergenceDataTest2$SeedingMetric<-as.numeric(as.character(EmergenceDataTest2$SeedingMetric))

#tiff("test.tiff", units="in", width=5.82, height=4.10, res=300)
ggplot(EmergenceDataTest2,aes(SeedingMetric,Soy_num_metric,color=Stage))+
  geom_smooth(method = "lm",se=F,size=.75)+
  geom_abline(intercept = 0, slope = .9, color="black", 
              linetype="dashed", size=.75)+
  geom_point()+
  labs(x=expression("Seeding rate (seeds"~ha^-1*')'),
       y=expression("Soybean density (plants"~ha^-1*')'),
       fill="Soybean\ngrowth stage")+
  theme_bw(base_size = 14)+
  theme(legend.position = "right")+
  scale_y_continuous(labels = scales::comma)+
  scale_x_continuous(labels = scales::comma,
                     breaks=c(0,185300,370700,556000,741300))
#dev.off()

EmergenceDataTest %>% 
  filter(Stage=="V1") %>% 
  group_by(SeedingMetric) %>% 
  summarize(MeanPlants=mean(Soy_num_metric))
```

##Yeild
  
-Yield calculated at 13% moisture and accounts for sampling method. This was only done for the final metric, SeedWeight_kgha.
-The full model does not work with nlme()
```{r Prep}
EmergenceData2<-EmergenceData[EmergenceData$Stage=="V1",]
EmergenceData2$Seeding<-as.numeric(as.character(EmergenceData2$Seeding))
EmergenceData2$Nitrogen<-factor(EmergenceData2$Nitrogen, levels = c("0","60","120"))
EmergenceData2$Site<-dplyr::recode(EmergenceData2$Site,"Aur"="Aurora","Gen"="Geneva")

YieldData3<-YieldData2
YieldData3$Site<-factor(YieldData3$Site,levels = c("Aur","Gen"),labels = c("Aurora","Geneva"))
YieldData3$Seeding<-as.numeric(as.character(YieldData3$Seeding))
YieldData3$Soy_num<-NULL
YieldData3$Block<-as.factor(YieldData3$Block)
YieldData3<-left_join(YieldData3,
          EmergenceData2[!EmergenceData2$Seeding==0,-which(names(EmergenceData2) %in% c("Stage"))])
YieldData3<-YieldData3 %>% 
  mutate(Soy_num_metric=Soy_num*2.47,
         SeedWeight_kgha=SeedWeight_g*(5.33/.001)*(2.47/1)*(1/1000)*
           (100/87)) #conversion to kg/ha; last fraction is moisture adju.

YieldData5<-YieldData
YieldData5<-YieldData5 %>% 
  mutate(Soy_num=(43560/(30/12)*(Soy_num/3.28084)))
YieldData5$Site<-factor(YieldData5$Site,levels = c("Aur","Gen"),labels = c("Aurora","Geneva"))
YieldData5$Seeding<-as.numeric(as.character(YieldData5$Seeding))
YieldData5$Soy_num<-NULL
YieldData5$Block<-as.factor(YieldData5$Block)
YieldData5<-left_join(YieldData5,
          EmergenceData2[,-which(names(EmergenceData2) %in% c("Stage"))])
YieldData5<-YieldData5 %>% 
  mutate(Soy_num_metric=Soy_num*2.47,
         SeedWeight_kgha=SeedWeight_g*(5.33/.001)*(2.47/1)*(1/1000)*
           (100/87),#conversion to kg/ha; last fraction is moisture adju.
         NitrogenMetric=case_when(
           Nitrogen==0~0,
           Nitrogen==60~70,
           Nitrogen==120~135))
YieldData5$NitrogenMetric<-as.factor(YieldData5$NitrogenMetric)
```

```{r yield Modeling}
#asymptotic
boxplot(YieldData5$SeedWeight_kgha)
##Reduced
Asy_Red<-nlme(data=YieldData5,
    SeedWeight_kgha~a*(1-exp(-exp(b)*Soy_num_metric)),
    start = c(a=3000,b=-11.8), #I had to change a to get a fit when I re-ran code in 2025
    fixed= list(a~1,b ~ 1),
    random = list(Site=pdDiag(list(a~1,b ~ 1)),
                  Block=pdDiag(list(a~1,b ~ 1))),
    na.action = na.omit)

##Site
AsySite_Semi<-nlme(data=YieldData5,
    SeedWeight_kgha~a*(1-exp(-exp(b)*Soy_num_metric)),
    start = c(3500,3000,-11.8),
    fixed= list(a~Site,b ~ 1),
    random = list(Site=pdDiag(list(a~Site,b ~ 1)),
                  Block=pdDiag(list(a~Site,b ~ 1))),
    na.action = na.omit)

#AsySite_Full<-nlme(data=YieldData5,
#    SeedWeight_kgha~a*(1-exp(-exp(b)*Soy_num_metric)),
#    start = c(3573.4,3152.2,-11.8,-11.8),
#    fixed= list(a+b ~ Site),
#    random = list(Site=pdDiag(list(a ~ Site,b~Site)),
#                  Block=pdDiag(list(a ~ Site,b~Site))),
#    na.action = na.omit,
#    control = list(pnlsTol = 1e-6,msMaxIter=5000))

anova(Asy_Red,AsySite_Semi)

library(sjPlot)
coef(summary(AsySite_Semi))
fixef(AsySite_Semi)[1]
#t.test(fixef(AsySite_Semi)[1]) not sure why this doesn't work
fun.1YieldSite<- function(x) fixef(Asy_Red)[1]*(1-exp(-exp(fixef(Asy_Red)[2])*x))
fun.2.1YieldSite<- function(x) fixef(AsySite_Semi)[1]*(1-exp(-exp(fixef(AsySite_Semi)[3])*x))
fun.2.2YieldSite<- function(x) (fixef(AsySite_Semi)[1]+fixef(AsySite_Semi)[2])*(1-exp(-exp(fixef(AsySite_Semi)[3])*x)) 


library(grid)
#Optimums where used in the publication
optimize(fun.2.1YieldSite, interval=c(0,741300),maximum = T)
optimize(fun.2.2YieldSite, interval=c(0,741300),maximum = T)

###Semi-reduced graph-Site
#tiff("Fig4.tiff", units="in", width=5.82, height=5.54, res=300)
ggplot(YieldData5,aes(x=Soy_num_metric,y=SeedWeight_kgha))+#,color=Site))+
    geom_point()+
    stat_function(fun=fun.1YieldSite,size=1.2)+
    theme_bw(base_size = 18)+
    labs(y=expression("Soybean yield (kg"~ha^-1*')'),
         x=expression("Soybean density (plants"~ha^-1*')'),
         color="Site")+
    scale_x_continuous(labels = scales::comma)+
    scale_color_brewer(palette = "Accent")+
    theme(legend.position = "bottom")
#dev.off()

##Nitrogen-FULL DOES NOT WORK
AsyNitrogen_Semi<-nlme(data=YieldData5,
    SeedWeight_kgha~a*(1-exp(-exp(b)*Soy_num_metric)),
    start = c(3500,3000,3000,-11.8),
    fixed= list(a~Nitrogen,b ~ 1),
    random = list(Site=pdDiag(list(a~Nitrogen,b ~ 1)),
                  Block=pdDiag(list(a~Nitrogen,b ~ 1))),
    na.action = na.omit)

#AsyNitrogen_Full<-nlme(data=YieldData5,
#    SeedWeight_kgha~a*(1-exp(-exp(b)*Soy_num_metric)),
#    start = c(3573.4,3152.2,3152.2,-11.8,-11.8,-11.8),
#    fixed= list(a+b ~ Nitrogen),
#    random = list(Site=pdDiag(list(a ~ Nitrogen,b~Nitrogen)),
#                  Block=pdDiag(list(a ~ Nitrogen,b~Nitrogen))),
#    na.action = na.omit,
#    control = list(pnlsTol = 1e-6,msMaxIter=5000))

anova(Asy_Red,AsyNitrogen_Semi)

fixef(Asy_Red)
fixef(AsySite_Semi)
fixef(AsyNitrogen_Semi)
```

#Weeds
```{r setup}
SR_weedsRaw<-read.xlsx(here("Data","SR_weedsRaw.xlsx"))
colnames(SR_weedsRaw)[6]<-"Biomass"
unique(SR_weedsRaw$Treatment)
summary(as.factor(SR_weedsRaw$Site))
table(SR_weedsRaw$Plot[SR_weedsRaw$Site=="Gen"],SR_weedsRaw$Treatment[SR_weedsRaw$Site=="Gen"])

SR_weedsRaw<-as.data.frame(
  pivot_wider(SR_weedsRaw,
            names_from = Weed,
            values_from = Biomass,
            values_fill = list(Biomass=0)))

#SR_weedsWide<-createWorkbook()
#addWorksheet(SR_weedsWide,"Wide")
#writeData(SR_weedsWide,"Wide",SR_weedsRaw2,rowNames = T)
#saveWorkbook(SR_weedsWide,"~/Box/Rye-Soybean 2019/Data/Weeds/SR_weedsWide.xlsx",overwrite = T)
SR_weedsWide<-read.xlsx(here("Data","SR_weedsWideEdited.xlsx"),sheet = 1)

SR_weedsWide<-SR_weedsWide %>% 
mutate(Seeding=ifelse(Site=="Aur" & 
                            Plot%in% c(1,9,14,17),300,
                          ifelse(Site=="Aur" & 
                                 Plot%in% c(2,6,13,19),225,
                                 ifelse(Site=="Aur" &
                                          Plot%in% c(4,8,12,20), 150,
                                        ifelse(Site=="Aur" &
                                                 Plot%in% c(5,7,15,18), 75,
                                               ifelse(Site=="Aur" &
                                                        Plot%in% c(3,10,11,16),0,
                    ifelse(Site=="Gen" & 
                             Plot%in% c(4,10,13,16),300,
                           ifelse(Site=="Gen" &
                                     Plot%in% c(1,8,14,17),225,
                                  ifelse(Site=="Gen" &
                                           Plot%in% c(3,7,15,19),150,
                                         ifelse(Site=="Gen" &
                                                  Plot%in% c(2,9,11,20),75,
                                                0)))))))))) %>%
  dplyr::select(Site,Block,Plot,Treatment,Seeding,everything())

#This is the seeding rate correction for the weeds data. All other analysis stems from this data frame.
SR_weedsWide[SR_weedsWide$Site=="Gen",]$Seeding<-
  dplyr::recode(SR_weedsWide[SR_weedsWide$Site=="Gen",]$Seeding,
         "150"="75", "75"="150","225"="300","300"="225", "0"="0")

SR_weedsKey<-read.xlsx(here("Data","SR_weedsWideEdited.xlsx"),sheet = 2)

SR_weedsLong<-as.data.frame(
  pivot_longer(SR_weedsWide,
               -c(Site,Block,Plot,Treatment,Seeding),
               names_to = "Species",
               values_to = "Biomass"))

SR_weedsBiomass<-
  as.data.frame(
  SR_weedsLong %>%
    group_by(Site,Block,Plot,Treatment,Seeding) %>%
    dplyr::select(-Species) %>% 
    summarise(TotalBiomass=sum(Biomass)))
SR_weedsBiomass[c("Site","Block","Treatment","Seeding")]<-lapply(SR_weedsBiomass[c("Site","Block","Treatment","Seeding")], factor)

SR_weedsBiomass$Seeding<-factor(SR_weedsBiomass$Seeding,levels = c("0","75","150","225","300"))
```
##Biomass
EmergenceData2 needs to be loaded.
Two outliers (weeds above 300 kg/ha) were removed for model convergence. 
```{r biomass modeling}
#Setup
SR_weedsBiomass2<-SR_weedsBiomass %>% 
  group_by(Site,Treatment, Seeding)%>% 
  mutate(Mean_lbs..ac=TotalBiomass*((.5/0.000123553)*.0022))
SR_weedsBiomass2$Treatment<-factor(SR_weedsBiomass2$Treatment,
                                   levels = c("None","Low","High"),
                                   labels = c("0","60","120"))
SR_weedsBiomass2<-rename(SR_weedsBiomass2,"Nitrogen"="Treatment")

SR_weedsBiomass3<-SR_weedsBiomass2
SR_weedsBiomass3$Seeding<-as.numeric(as.character(SR_weedsBiomass3$Seeding))
SR_weedsBiomass3$Site<-dplyr::recode(SR_weedsBiomass3$Site,"Aur"="Aurora","Gen"="Geneva")
SR_weedsBiomass3<-
  left_join(SR_weedsBiomass3,EmergenceData2, by = c("Site", "Block", "Plot",
                                                    "Nitrogen", "Seeding"))
BiomassData2<-BiomassData2 %>% 
  dplyr::select(-c(Plant,'Soy#'))
SR_weedsBiomass3<-
  left_join(SR_weedsBiomass3,BiomassData2, by = c("Site", "Block", "Plot",
                                                  "Nitrogen", "Seeding"))

SR_weedsBiomass3<-SR_weedsBiomass3 %>% 
  mutate(Soy_num_metric=Soy_num*2.47105,
         TotalBiomass_metric=TotalBiomass*(2.47105/2.20462),
         log_TotalBiomass_metric=log(TotalBiomass_metric),
         sqrt_TotalBiomass_metric=sqrt(TotalBiomass_metric))

SR_weedsBiomass3<-SR_weedsBiomass3 %>% 
  mutate(NitrogenMetric=case_when(Nitrogen==60~70,
                                  Nitrogen==120~135,
                                  TRUE~0))
#Outliers
boxplot(SR_weedsBiomass3$TotalBiomass_metric)
grubbs.test(SR_weedsBiomass3$TotalBiomass_metric)

#Info
range(SR_weedsBiomass3$TotalBiomass_metric,na.rm = T)

SR_weedsBiomass3 %>% 
  filter(Seeding==0) %>% 
  group_by(Nitrogen) %>% 
  summarise(Mean=mean(TotalBiomass_metric,na.rm=T))

#Site - No effect
Weed_Red<-
  nlme(data = SR_weedsBiomass3[SR_weedsBiomass3$TotalBiomass_metric<300,],
     TotalBiomass_metric~
       w0/(1+i*Soy_num_metric),
     start = c(1.793565e+02,4.584e-06),
     fixed= list(w0~1,i ~ 1),
     random = list(Site=pdDiag(list(w0~1,i ~ 1)),
                   Block=pdDiag(list(w0~1,i ~ 1))),
     na.action = na.omit)

Weed_SemiSite<-
  nlme(data = SR_weedsBiomass3[SR_weedsBiomass3$TotalBiomass_metric<300,],
     TotalBiomass_metric~
       w0/(1+i*Soy_num_metric),
     start = c(1.793565e+02,1.793565e+02,4.584e-06),
     fixed= list(w0~Site,i ~ 1),
     random = list(Site=pdDiag(list(w0~Site,i ~ 1)),
                   Block=pdDiag(list(w0~Site,i ~ 1))),
     na.action = na.omit)

Weed_FullSite<-
  nlme(data = SR_weedsBiomass3[SR_weedsBiomass3$TotalBiomass_metric<300,],
     TotalBiomass_metric~
       w0/(1+i*Soy_num_metric),
     start = c(w0=1.793565e+02,0,0, i=4.584e-06),
     fixed= list(w0+i ~ Site),
     random = list(Site=pdDiag(list(w0~Site,i ~ Site)),
                   Block=pdDiag(list(w0~Site,i ~ Site))),
     na.action = na.omit)

anova(Weed_Red,Weed_SemiSite)
anova(Weed_Red,Weed_FullSite)
anova(Weed_SemiSite,Weed_FullSite)

#Nitrogen effect - semi is best
Weed_SemiNitrogen<-
  nlme(data = SR_weedsBiomass3[SR_weedsBiomass3$TotalBiomass_metric<300,],
     TotalBiomass_metric~
       w0/(1+i*Soy_num_metric),
     start = c(1.793565e+02,1.793565e+02,1.793565e+02,4.584e-06),
     fixed= list(w0~Nitrogen,i ~ 1),
     random = list(Site=pdDiag(list(w0~Nitrogen,i ~ 1)),
                   Block=pdDiag(list(w0~Nitrogen,i ~ 1))),
     na.action = na.omit)

###Estimates for fitting
TestList<-nlsList(data = SR_weedsBiomass3,
     TotalBiomass_metric~
       w0/(1+i*Soy_num_metric)|Nitrogen,
     start = c(w0=1.793565e+02,i=4.584e-06),
     na.action = na.omit)
###

Weed_FullNitrogen<-
  nlme(data = SR_weedsBiomass3[SR_weedsBiomass3$TotalBiomass_metric<300,],
     TotalBiomass_metric~
       w0/(1+i*Soy_num_metric),
     start = c(coef(TestList)[1,1],coef(TestList)[2,1],coef(TestList)[3,1],
               coef(TestList)[1,2],coef(TestList)[2,2],coef(TestList)[3,2]),
     fixed= list(w0+i ~ Nitrogen),
     random = list(Site=pdDiag(w0+i ~ Nitrogen),
                   Block=pdDiag(w0+i ~ Nitrogen)),
     na.action = na.omit)

anova(Weed_Red,Weed_SemiNitrogen)
anova(Weed_SemiNitrogen,Weed_FullNitrogen)
anova(Weed_Red,Weed_FullNitrogen)

fixef(Weed_Red)
fixef(Weed_SemiSite)
fixef(Weed_SemiNitrogen)
fixef(Weed_FullSite)
fixef(Weed_FullNitrogen)

plot(Weed_SemiNitrogen)
qqnorm(Weed_SemiNitrogen,abline = c(0,1))

WeedModFE<-fixef(Weed_SemiNitrogen)
fun.1nit<-function(x) WeedModFE[1]*(1/(1+(WeedModFE[4]*x)))
fun.2nit<-function(x) (WeedModFE[1]+WeedModFE[2])*(1/(1+(WeedModFE[4]*x)))
fun.3nit<-function(x) (WeedModFE[1]+WeedModFE[3])*(1/(1+(WeedModFE[4]*x)))

#tiff("Fig2.tiff", units="in", width=5.82, height=5.54, res=300)
#pdf("Fig2.pdf", width=5.82, height=5.54)
ggplot(SR_weedsBiomass3,
       aes(x=Soy_num_metric,y=TotalBiomass_metric,color=as.factor(NitrogenMetric)))+
    geom_point()+
    stat_function(fun=fun.1nit,size=1.2,aes(color="0"))+
    stat_function(fun=fun.2nit,size=1.2,aes(color="70"))+
    stat_function(fun=fun.3nit,size=1.2,aes(color="135"))+
    theme_bw(base_size = 18)+
    ylab(expression("Weed biomass (kg"~ha^-1*')'))+
    xlab(expression("Soybean density (plants"~ha^-1*')'))+
    labs(color=expression("Nitrogen (kg"~ha^-1*')'))+
    scale_y_continuous(labels = scales::comma)+
    scale_x_continuous(labels = scales::comma)+
    scale_color_brewer(palette = "Accent",labels = c("0", "63", "125"))+
    theme(plot.title = element_text(hjust = 0.5), 
          legend.position = "bottom")
#dev.off()

fun.1RedTest<-function(x) fixef(Weed_Red)[1]*(1/(1+(fixef(Weed_Red)[2]*x)))

#pdf("Fig2Mod.pdf", width=5.82, height=5.54)
ggplot(SR_weedsBiomass3,
       aes(x=Soy_num_metric,y=TotalBiomass_metric))+
    geom_point()+
    stat_function(fun=fun.1RedTest,size=1.2)+
    theme_bw(base_size = 18)+
    ylab(expression("Weed biomass (kg"~ha^-1*')'))+
    xlab(expression("Soybean density (plants"~ha^-1*')'))+
    scale_y_continuous(labels = scales::comma)+
    scale_x_continuous(labels = scales::comma)+
    theme(plot.title = element_text(hjust = 0.5), 
          legend.position = "bottom")
#dev.off()


WeedModFE2 <- fixef(Weed_FullNitrogen)
fun.1FullTest<-function(x) WeedModFE2[1]*(1/(1+(WeedModFE2[4]*x)))
fun.2FullTest<-function(x) WeedModFE2[2]*(1/(1+(WeedModFE2[5]*x)))
fun.3FullTest<-function(x) WeedModFE2[3]*(1/(1+(WeedModFE2[6]*x)))

#pdf("Fig2Mod.pdf", width=5.82, height=5.54)
ggplot(SR_weedsBiomass3,
       aes(x=Soy_num_metric,y=TotalBiomass_metric,color=as.factor(NitrogenMetric)))+
    geom_point()+
    stat_function(fun=fun.1FullTest,size=1.2,aes(color="0"))+
    stat_function(fun=fun.2FullTest,size=1.2,aes(color="70"))+
    stat_function(fun=fun.3FullTest,size=1.2,aes(color="135"))+
    theme_bw(base_size = 18)+
    ylab(expression("Weed biomass (kg"~ha^-1*')'))+
    xlab(expression("Soybean density (plants"~ha^-1*')'))+
    labs(color=expression("Nitrogen (kg"~ha^-1*')'))+
    scale_y_continuous(labels = scales::comma)+
    scale_x_continuous(labels = scales::comma)+
    scale_color_brewer(palette = "Accent",labels = c("0", "63", "125"))+
    theme(plot.title = element_text(hjust = 0.5), 
          legend.position = "bottom")
#dev.off()

```

##System
I had to switch transform = response to type = response in emmeans to get things to run Fig results did not change (3/1/23). But its possible that's because letters were manually input (back from when transform = response worked). 
```{r Annual vs. Perennial, eval=FALSE, include=FALSE}
SR_weedsLong
SR_weedsKey
SR_weedsLong$Species<-gsub("\\."," ",SR_weedsLong$Species)
SR_weedsLong$Species<-dplyr::recode(SR_weedsLong$Species,"Tree spp "="Tree spp.")

SR_weedsJoined<-left_join(SR_weedsLong,SR_weedsKey,by = c("Species" = "Common.Name"))
SR_weedsJoinedNoNA<-SR_weedsJoined[-which(is.na(SR_weedsJoined$LifeCycle)),]

SR_weedsBiomass_Joined<-
  as.data.frame(
  SR_weedsJoinedNoNA %>%
    group_by(Site,Block,Plot,Treatment,Seeding,LifeCycle,Habit) %>%
    dplyr::select(-Species) %>% 
    summarise(TotalBiomass=sum(Biomass)) %>% 
    mutate(Mean_lbs..ac=TotalBiomass*((.5/0.000123553)*.0022),
           WeedBiomass_kgha=(TotalBiomass/.5)*10,
           NitrogenMetric=
             case_when(Treatment=="Low"~70,
                       Treatment=="High"~135,
                       TRUE~0))%>% 
    dplyr::rename("Nitrogen"="Treatment"))

SR_weedsBiomass_Joined[c("Site","Block","Nitrogen","Seeding","LifeCycle","Habit")]<-
  lapply(SR_weedsBiomass_Joined[c("Site","Block","Nitrogen","Seeding","LifeCycle","Habit")], factor)

SR_weedsBiomass_Joined$Nitrogen<-
  factor(SR_weedsBiomass_Joined$Nitrogen,
         levels=c("None","Low","High"),
         labels = c("0","60","120"))
SR_weedsBiomass_Joined$Habit<-
  factor(SR_weedsBiomass_Joined$Habit,
         levels=c("BL","G"),
         labels = c("Broadleaf","Grass"))
SR_weedsBiomass_Joined$NitrogenMetric<-as.factor(SR_weedsBiomass_Joined$NitrogenMetric)

SysWeedBiomass<-SR_weedsBiomass_Joined
str(SysWeedBiomass)
SysWeedBiomass$Site<-factor(SysWeedBiomass$Site,levels = c("Aur","Gen"),labels = c("Aurora","Geneva"))
SysWeedBiomass$Seeding<-as.numeric(as.character(SysWeedBiomass$Seeding))

#Avg, perennial weed biomass in the control! For dissertation!
SR_weedsBiomass_Joined %>% 
  filter(Nitrogen == 0 & Seeding == 0 & LifeCycle == "Perennial") %>% 
  group_by(Site,LifeCycle,Block,Plot) %>% 
  summarise(WeedBio2=sum(WeedBiomass_kgha,na.rm=T)) %>% 
  ungroup() %>% 
  summarise(Mean=mean(WeedBio2,na.rm=T))

SR_weedsBiomass_Joined2<-SR_weedsBiomass_Joined
SR_weedsBiomass_Joined2$Site<-factor(SR_weedsBiomass_Joined2$Site,
                                     levels = c("Aur","Gen"),
                                     labels = c("Aurora","Geneva"))
library(plotrix)
Vect<-SR_weedsBiomass_Joined2 %>%
  filter(!Seeding==0) %>% 
  group_by(Site,LifeCycle,NitrogenMetric) %>% 
  summarise(MaxBar=mean(WeedBiomass_kgha,na.rm=T)+
              std.error(WeedBiomass_kgha,na.rm=T))

#tiff("Fig3_Dissertation.tiff", units="in", width=7.81, height=3.55, res=300)
ggplot(SR_weedsBiomass_Joined2[!SR_weedsBiomass_Joined2$Seeding==0,],
       aes(LifeCycle,WeedBiomass_kgha,fill=NitrogenMetric))+
  stat_summary(geom = "bar",fun="mean",na.rm=TRUE,position = "dodge")+
  stat_summary(geom = "errorbar",fun.data = "mean_se",na.rm = TRUE,
               width=.1,position = position_dodge(.9))+
  geom_text(data=Vect,aes(x=LifeCycle,y=MaxBar),
            label=c("a","b","b","a","a","b",
                    "a","a","b","a","a","a"),
            position = position_dodge(.9),
            vjust=-.45,size=4.5)+
  coord_cartesian(ylim=c(0,1200))+
  labs(fill = expression("Nitrogen (kg"~ha^-1*')'))+
  theme_bw(base_size = 16)+
  scale_fill_grey(start = 0.8, end = 0.4,labels = c("0", "63", "125"))+
  scale_y_continuous(labels = scales::comma)+
  theme(legend.position = "right")+
  xlab("Weed lifecycle")+
  ylab(expression("Weed biomass (kg"~ha^-1*')'))+
  facet_wrap(~Site)
#dev.off()

SR_weedsBiomass_Joined2$Block<-as.numeric(as.character(SR_weedsBiomass_Joined2$Block))

SR_weedsBiomass_Joined3<-SR_weedsBiomass_Joined2 %>% 
  group_by(Site,Block,Plot,Seeding, NitrogenMetric,LifeCycle) %>% 
  summarise(WeedBiomass_kgha=sum(WeedBiomass_kgha)) %>% 
  mutate(Block=case_when(
    Site=="Geneva"~Block+4,
    TRUE~Block
  ))
SR_weedsBiomass_Joined2$Block<-as.factor(SR_weedsBiomass_Joined2$Block)
SR_weedsBiomass_Joined3$Block<-as.factor(SR_weedsBiomass_Joined3$Block)
SR_weedsBiomass_Joined3 %>% 
  filter(LifeCycle=="Perennial"&WeedBiomass_kgha=="0")

#WITH INT linear model supplementation 
AnnualBiomassAur<-lmer(sqrt(WeedBiomass_kgha)~Seeding*NitrogenMetric+
                      (1|Block/Seeding),
     data = SR_weedsBiomass_Joined3[SR_weedsBiomass_Joined3$LifeCycle=="Annual"&
                                    SR_weedsBiomass_Joined3$Site=="Aurora"&
                                    !SR_weedsBiomass_Joined3$Seeding==0,])
plot(AnnualBiomassAur)
anova(AnnualBiomassAur)
multcomp::cld(emmeans(AnnualBiomassAur,specs = ~NitrogenMetric, type = "response"),
            sort=F,adjust="none",Letters="abcd")

AnnualBiomassGen<-lmer(sqrt(WeedBiomass_kgha)~Seeding*NitrogenMetric+
                      (1|Block/Seeding),
     data = SR_weedsBiomass_Joined3[SR_weedsBiomass_Joined3$LifeCycle=="Annual"&
                                    SR_weedsBiomass_Joined3$Site=="Geneva"&
                                    !SR_weedsBiomass_Joined3$Seeding==0,])
plot(AnnualBiomassGen)
anova(AnnualBiomassGen)
multcomp::cld(emmeans(AnnualBiomassGen,specs = ~NitrogenMetric,type = "response"),
            sort=F,adjust="none",Letters="abcd")

PerennialBiomassAur<-lmer(sqrt(WeedBiomass_kgha)~Seeding*NitrogenMetric+
                      (1|Block/Seeding),
     data = SR_weedsBiomass_Joined3[SR_weedsBiomass_Joined3$LifeCycle=="Perennial"&
                                    SR_weedsBiomass_Joined3$Site=="Aurora"&
                                    !SR_weedsBiomass_Joined3$Seeding==0,])
plot(PerennialBiomassAur)
anova(PerennialBiomassAur)
multcomp::cld(emmeans(PerennialBiomassAur,specs = ~NitrogenMetric,type = "response"),
            sort=F,adjust="none",Letters="abcd")

PerennialBiomassGen<-lmer(sqrt(WeedBiomass_kgha)~Seeding*NitrogenMetric+
                      (1|Block/Seeding),
     data = SR_weedsBiomass_Joined3[SR_weedsBiomass_Joined3$LifeCycle=="Perennial"&
                                    SR_weedsBiomass_Joined3$Site=="Geneva"&
                                    !SR_weedsBiomass_Joined3$Seeding==0,])
plot(PerennialBiomassGen)
anova(PerennialBiomassGen)
multcomp::cld(emmeans(PerennialBiomassGen,specs = ~NitrogenMetric,type = "response"),
            sort=F,adjust="none",Letters="abcd")

library(glmmTMB)
library(DHARMa)

Tester<-lmer((WeedBiomass_kgha)~Site*Seeding*NitrogenMetric+(1|Site:Block),
     data = SR_weedsBiomass_Joined3[SR_weedsBiomass_Joined3$LifeCycle=="Perennial",])
Tester2<-glmmTMB(WeedBiomass_kgha~Site*Seeding*NitrogenMetric+(1|Site:Block),
                 family = tweedie(),
                 data = SR_weedsBiomass_Joined3[SR_weedsBiomass_Joined3$LifeCycle=="Perennial",])
simulateResiduals(Tester2, plot = TRUE)
car::Anova(Tester2,type=3)
```

##Community
```{r PERMANOVA all, eval=FALSE, include=FALSE}
SR_sp<-SR_weedsWide %>% dplyr::select(-c(Site,Block,Plot,Treatment,Seeding)) 
SR_env<-SR_weedsWide %>% dplyr::select(Site,Block,Plot,Treatment,Seeding) 
SR_env[c("Site","Block","Treatment","Seeding")]<-lapply(SR_env[c("Site","Block","Treatment","Seeding")], factor)
SR_sp<-SR_sp[-c(72,110),]#this data was missing, I removed it
SR_env<-SR_env[-c(72,110),]
SR_sp[is.na(SR_sp)]<-0 #this data should have been 0, I corrected it
any(is.na(SR_sp))

nmds_SR<-metaMDS(SR_sp,try=50,trymax = 100)
dimcheckMDS(SR_sp)
stressplot(nmds_SR)

op_SR <- ordiplot(nmds_SR, type = "n")
cols <- c('#e66101','#5e3c99')
points(nmds_SR, cex = 1, pch = 16, col = cols[SR_env$Site])
ordispider(nmds_SR, groups = SR_env$Site,label = T)
ordihull(nmds_SR, groups = SR_env$Site, lty = "dotted")

#Sites had significantly different dispersion. This was also apparent when looking at the nmds of the weed data when grouped as a function of site.
bd_SR.Site <- betadisper(vegdist(SR_sp, method = "bray"), SR_env$Site)
boxplot(bd_SR.Site)
anova(bd_SR.Site)
permutest(bd_SR.Site)

SR_sp0<-SR_weedsWide %>% 
  filter(Seeding %in% c(75,150,225,300)) %>%
  dplyr::select(-c(Site,Block,Plot,Treatment,Seeding)) 
SR_env0<-SR_weedsWide %>% 
  filter(Seeding %in% c(75,150,225,300)) %>% 
  dplyr::select(Site,Block,Plot,Treatment,Seeding) 
SR_env0[c("Site","Block","Treatment","Seeding")]<-
  lapply(SR_env0[c("Site","Block","Treatment","Seeding")], factor)

SR_sp0<-SR_sp0[-c(72,110),]#this data was missing, I removed it
SR_env0<-SR_env0[-c(72,110),]
SR_sp0[is.na(SR_sp0)]<-0 #this data should have been 0, I corrected it
any(is.na(SR_sp0))

bd_SR0.Site <- betadisper(vegdist(SR_sp0, method = "bray"), SR_env0$Site)
boxplot(bd_SR0.Site)
anova(bd_SR0.Site)
permutest(bd_SR0.Site)
```

```{r PERMANOVA Aurora, eval=FALSE, include=FALSE}
SR_spAur<-SR_weedsWide %>% 
  filter(Site=="Aur") %>% 
  dplyr::select(-c(Site,Block,Plot,Treatment,Seeding)) 
SR_envAur<-SR_weedsWide %>% 
  filter(Site=="Aur") %>%
  dplyr::select(Site,Block,Plot,Treatment,Seeding) 
SR_envAur[c("Site","Block","Treatment","Seeding")]<-
  lapply(SR_envAur[c("Site","Block","Treatment","Seeding")], factor)

SR_spAur0<-SR_weedsWide %>% 
  filter(Site=="Aur",Seeding %in% c(75,150,225,300)) %>%
  dplyr::select(-c(Site,Block,Plot,Treatment,Seeding)) 
SR_envAur0<-SR_weedsWide %>% 
  filter(Site=="Aur",Seeding %in% c(75,150,225,300)) %>%
  dplyr::select(Site,Block,Plot,Treatment,Seeding) 
SR_envAur0[c("Site","Block","Treatment","Seeding")]<-
  lapply(SR_envAur0[c("Site","Block","Treatment","Seeding")], factor)

nmds_SR.Aur<-metaMDS(SR_spAur,try=50,trymax = 100,k=2)
dimcheckMDS(SR_spAur)
stressplot(nmds_SR.Aur)

#Assumption testing: Nitrogen rate looks good
#library(vegan3d)
#nmds_SR.Aur3d<-metaMDS(SR_spAur,try=50,trymax = 100,k=3)
#op_SR <- ordiplot3d(nmds_SR.Aur3d, type = "n")
#cols <- c('#b35806','#e08214','#fdb863')
#points(nmds_SR.Aur, cex = 1, pch = 16, col = cols[SR_envAur$Treatment])
#ordispider(nmds_SR.Aur, groups = SR_envAur$Treatment,label = T)
#ordihull(nmds_SR.Aur, groups = SR_envAur$Treatment, lty = "dotted")

#non-zero rates- perfect
bd_SR_Aur_Treatment <- betadisper(vegdist(SR_spAur0, method = "bray"), SR_envAur0$Treatment)
boxplot(bd_SR_Aur_Treatment)
anova(bd_SR_Aur_Treatment)
permutest(bd_SR_Aur_Treatment)

##Assumption testing: Seeding rate looks good
#All five seeding rates
#op_SR <- ordiplot(nmds_SR.Aur, type = "n")
#cols <- c('#b35806','#e08214','#fdb863')
#points(nmds_SR.Aur, cex = 1, pch = 16, col = cols[SR_envAur$Seeding])
#ordispider(nmds_SR.Aur, groups = SR_envAur$Seeding,label = T)
#ordihull(nmds_SR.Aur, groups = SR_envAur$Seeding, lty = "dotted")

#bd_SR_Aur_Seeding <- betadisper(vegdist(SR_spAur, method = "bray"), SR_envAur$Seeding)
#boxplot(bd_SR_Aur_Seeding)
#anova(bd_SR_Aur_Seeding)
#permutest(bd_SR_Aur_Seeding)

#non-zero rates- perfect
bd_SR_Aur_Seeding0 <- betadisper(vegdist(SR_spAur0, method = "bray"), SR_envAur0$Seeding)
boxplot(bd_SR_Aur_Seeding0)
anova(bd_SR_Aur_Seeding0)
permutest(bd_SR_Aur_Seeding0)

#library(vegan3d)
#library(rgl)

#ordirgl(nmds_SR.Aur3d,groups = SR_envAur$Seeding,col = SR_envAur$Seeding)
#orglspider (nmds_SR.Aur3d, groups = SR_envAur$Seeding,label = T)
#orglellipse (nmds_SR.Aur3d, groups = SR_envAur$Seeding,col = SR_envAur$Seeding)
#movie3d(spin3d(axis = c(0, .5, .5)), 
        #duration = 3,
        #dir = getwd())

####PERMANOVA####
PermSetAur<- how(within = Within(type = "free"),
         plots = Plots(strata = interaction(SR_envAur0$Block,SR_envAur0$Seeding), 
                       type = "free"),
         blocks = SR_envAur0$Block,nperm=999)

pmv_SR_Aur_BreyCurtis <- adonis2(
  SR_spAur ~ Seeding*Treatment, data = SR_envAur)
pmv_SR_Aur_BreyCurtis

pmv_SR_Aur_BreyCurtis0b <- adonis2(
  SR_spAur0 ~ Seeding*Treatment, data = SR_envAur0,permutations = PermSetAur)
pmv_SR_Aur_BreyCurtis0b
```

```{r PERMANOVA Geneva, eval=FALSE, include=FALSE}
SR_spGen<-SR_weedsWide %>%
  filter(Site=="Gen") %>%
  dplyr::select(-c(Site,Block,Plot,Treatment,Seeding)) 

SR_envGen<-SR_weedsWide %>%
  filter(Site=="Gen") %>%
  dplyr::select(Site,Block,Plot,Treatment,Seeding) 
SR_envGen[c("Site","Block","Treatment","Seeding")]<-lapply(SR_envGen[c("Site","Block","Treatment","Seeding")], factor)

SR_spGen<-SR_spGen[-c(12,50),]
SR_envGen<-SR_envGen[-c(12,50),]
SR_spGen[is.na(SR_spGen)]<-0 #this data should have been 0, I corrected it
any(is.na(SR_spGen))

#imputed
SR_weedsWide2<-SR_weedsWide
SR_weedsWide2[c(72,110),]
SR_weedsWide2[72,6:56]<-SR_weedsWide %>% 
  filter(Site=="Gen"&Treatment=="High"&Seeding==225) %>% 
  summarise_at(6:56,mean,na.rm=T)

SR_weedsWide2[110,6:56]<-SR_weedsWide %>% 
  filter(Site=="Gen"&Treatment=="High"&Seeding==300) %>% 
  summarise_at(6:56,mean,na.rm=T)

#Excluding zero AND imputed (12/29/20)
SR_spGen0<-SR_weedsWide2 %>% 
  filter(Site=="Gen",Seeding %in% c(75,150,225,300)) %>% 
  dplyr::select(-c(Site,Block,Plot,Treatment,Seeding)) 

SR_envGen0<-SR_weedsWide2 %>% 
  filter(Site=="Gen",Seeding %in% c(75,150,225,300)) %>%
  dplyr::select(Site,Block,Plot,Treatment,Seeding) 
SR_envGen0[c("Site","Block","Treatment","Seeding")]<-lapply(SR_envGen0[c("Site","Block","Treatment","Seeding")], factor)

#SR_spGen0<-SR_spGen0[-c(12,41),] #not nessary with imputed data
#SR_envGen0<-SR_envGen0[-c(12,41),] #not nessary with imputed data
SR_spGen0[is.na(SR_spGen0)]<-0 #this data should have been 0, I corrected it
any(is.na(SR_spGen0))


nmds_SR.Gen<-metaMDS(SR_spGen0,try=50,trymax = 100,k=2)
dimcheckMDS(SR_spGen0)
stressplot(nmds_SR.Gen)

#Assumption testing: Nitrogen rate looks good, especially without zero seeding rate
op_SR <- ordiplot(nmds_SR.Gen, type = "n")
cols <- c('#b35806','#e08214','#fdb863')
points(nmds_SR.Gen, cex = 1, pch = 16, col = cols[SR_envGen0$Treatment])
ordispider(nmds_SR.Gen, groups = SR_envGen0$Treatment,label = T)
ordihull(nmds_SR.Gen, groups = SR_envGen0$Treatment, lty = "dotted")

bd_SR_Gen_Treatment <- betadisper(vegdist(SR_spGen0, method = "bray"),
                                  SR_envGen0$Treatment)
boxplot(bd_SR_Gen_Treatment)
anova(bd_SR_Gen_Treatment)
permutest(bd_SR_Gen_Treatment)

##Assumption testing: Seeding rate looks good
#All five rates
#op_SR <- ordiplot(nmds_SR.Gen, type = "n")
#cols <- c('#b35806','#e08214','#fdb863')
#points(nmds_SR.Gen, cex = 1, pch = 16, col = cols[SR_envGen$Seeding])
#ordispider(nmds_SR.Gen, groups = SR_envGen$Seeding,label = T)
#ordihull(nmds_SR.Gen, groups = SR_envGen$Seeding, lty = "dotted")

#bd_SR_Gen_Seeding <- betadisper(vegdist(SR_spGen, method = "bray"), SR_envGen$Seeding)
#boxplot(bd_SR_Gen_Seeding)
#anova(bd_SR_Gen_Seeding)
#permutest(bd_SR_Gen_Seeding)

#Excluding the zero rate
bd_SR_Gen_Seeding0 <- betadisper(vegdist(SR_spGen0, method = "bray"), SR_envGen0$Seeding)
boxplot(bd_SR_Gen_Seeding0)
anova(bd_SR_Gen_Seeding0)
permutest(bd_SR_Gen_Seeding0)
#ordirgl(nmds_SR.Gen,groups = SR_envGen$Treatment,col = SR_envGen$Treatment)
#orglspider (nmds_SR.Gen, groups = SR_envGen$Treatment,label = T)
#orglellipse (nmds_SR.Gen, groups = SR_envGen$Treatment,col = SR_envGen$Treatment)
#movie3d(spin3d(axis = c(0, .5, .5)), 
        #duration = 3,
        #dir = getwd())

####PERMANOVA####
PermSetGen <- how(within = Within(type = "free"),
         plots = Plots(strata = interaction(SR_envGen0$Block,SR_envGen0$Seeding), 
                       type = "free"),
         blocks = SR_envGen0$Block,nperm=999)

pmv_SR_Gen_BreyCurtis <- adonis2(
  SR_spGen ~ Seeding*Treatment, data = SR_envGen)
pmv_SR_Gen_BreyCurtis

pmv_SR_Gen_BreyCurtis0b <- adonis2(
  SR_spGen0 ~ Seeding*Treatment, data = SR_envGen0,permutations = PermSetGen)
pmv_SR_Gen_BreyCurtis0b
```

```{r Dominance, eval=FALSE, include=FALSE}
#library(indicspecies)
#IndiAur0_Nit<-multipatt(SR_spAur0,SR_envAur0$Treatment,duleg=TRUE,func="IndVal",
 #                      control = how(nperm=99999))
#IndiGen0_Nit<-multipatt(SR_spGen0,SR_envGen0$Treatment,duleg=TRUE,func="IndVal",
 #                      control = how(nperm=99999))

#summary(IndiAur0_Nit)
#summary(IndiGen0_Nit)

library(labdsv)
#All data
labdsv::importance(SR_spAur,SR_envAur$Treatment,typical = FALSE)
labdsv::importance(SR_spGen,SR_envGen$Treatment,typical = FALSE)

Aur_ImpTable<-read.xlsx(here("Data","WeedDominanceDataAll.xlsx"),sheet = 1)#Just the results of the importance function
Gen_ImpTable<-read.xlsx(here("Data","WeedDominanceDataAll.xlsx"),sheet = 2)#Just the results of the importance function

Aur_ImpTable<-Aur_ImpTable %>% 
  pivot_longer(cols = c("High","Low","None"),names_to = "Nitrogen",values_to = "Total.Biomass") %>% 
  group_by(Nitrogen) %>% 
  arrange(Nitrogen,desc(Total.Biomass)) %>% 
  mutate(cumulative_percentage=100*cumsum(Total.Biomass)/sum(Total.Biomass),
         Site="Aurora") %>% 
  filter(cumulative_percentage<=90)
Aur_ImpTable$Species<-gsub("\\."," ",Aur_ImpTable$Species)

Gen_ImpTable<-Gen_ImpTable %>% 
  pivot_longer(cols = c("High","Low","None"),
               names_to = "Nitrogen",values_to = "Total.Biomass") %>% 
  group_by(Nitrogen) %>% 
  arrange(Nitrogen,desc(Total.Biomass)) %>% 
  mutate(cumulative_percentage=100*cumsum(Total.Biomass)/sum(Total.Biomass),
         Site="Geneva") %>% 
  filter(cumulative_percentage<=90)
Gen_ImpTable$Species<-gsub("\\."," ",Gen_ImpTable$Species)

Aur_ImpTable<-left_join(Aur_ImpTable,SR_weedsKey,by=c("Species"="Common.Name"))
Gen_ImpTable<-left_join(Gen_ImpTable,SR_weedsKey,by=c("Species"="Common.Name"))

ImpTable<-rbind(Aur_ImpTable,Gen_ImpTable)

ImpTable<-ImpTable %>% 
  mutate(WeedBiomass_kgha=Total.Biomass*20,
         NitrogenMetric=
           case_when(
             Nitrogen=="None"~0,
             Nitrogen=="Low"~63,
             Nitrogen=="High"~125)) %>% 
  dplyr::select(Site,NitrogenMetric,Scientific.name,LifeCycle,WeedBiomass_kgha,cumulative_percentage)

#Importance excluding 0
labdsv::importance(SR_spAur0,typical = FALSE,sort=TRUE)
labdsv::importance(SR_spGen0,typical = FALSE)

labdsv::importance(SR_spAur0,SR_envAur0$Treatment,typical = FALSE)
labdsv::importance(SR_spGen0,SR_envGen0$Treatment,typical = FALSE)

Aur0_ImpTable<-read.xlsx(here("Data", "WeedDominanceData.xlsx"),sheet = 1)#Just the results of the importance function
Gen0_ImpTable<-read.xlsx(here("Data","WeedDominanceData.xlsx"),sheet = 2)#Just the results of the importance function

Aur0_ImpTable<-Aur0_ImpTable %>% 
  pivot_longer(cols = c("High","Low","None"),names_to = "Nitrogen",values_to = "Total.Biomass") %>% 
  group_by(Nitrogen) %>% 
  arrange(Nitrogen,desc(Total.Biomass)) %>% 
  mutate(cumulative_percentage=100*cumsum(Total.Biomass)/sum(Total.Biomass),
         Site="Aurora") %>% 
  filter(cumulative_percentage<=90)
Aur0_ImpTable$Species<-gsub("\\."," ",Aur0_ImpTable$Species)

Gen0_ImpTable<-Gen0_ImpTable %>% 
  pivot_longer(cols = c("High","Low","None"),
               names_to = "Nitrogen",values_to = "Total.Biomass") %>% 
  group_by(Nitrogen) %>% 
  arrange(Nitrogen,desc(Total.Biomass)) %>% 
  mutate(cumulative_percentage=100*cumsum(Total.Biomass)/sum(Total.Biomass),
         Site="Geneva") %>% 
  filter(cumulative_percentage<=90)
Gen0_ImpTable$Species<-gsub("\\."," ",Gen0_ImpTable$Species)

Aur0_ImpTable<-left_join(Aur0_ImpTable,SR_weedsKey,by=c("Species"="Common.Name"))
Gen0_ImpTable<-left_join(Gen0_ImpTable,SR_weedsKey,by=c("Species"="Common.Name"))

ImpTable<-rbind(Aur0_ImpTable,Gen0_ImpTable)

ImpTable<-ImpTable %>% 
  mutate(WeedBiomass_kgha=Total.Biomass*20,
         NitrogenMetric=
           case_when(
             Nitrogen=="None"~0,
             Nitrogen=="Low"~70,
             Nitrogen=="High"~135)) %>% 
  dplyr::select(Site,NitrogenMetric,Scientific.name,LifeCycle,WeedBiomass_kgha,cumulative_percentage)

#Evenness
SR_sp2<-SR_weedsWide2 %>% 
  dplyr::select(-c(Site,Block,Plot,Treatment,Seeding))

SR_env2<-SR_weedsWide2 %>% 
  dplyr::select(Site,Block,Plot,Treatment,Seeding) 
SR_env2[c("Site","Block","Treatment","Seeding")]<-lapply(SR_env2[c("Site","Block","Treatment","Seeding")], factor)

#final cleaning
SR_env2$Block<-as.numeric(as.character(SR_env2$Block))
SR_env2<-SR_env2 %>% 
  mutate(Block=case_when(
    Site=="Gen" ~ Block+4,
    TRUE~Block))
SR_env2$Block<-as.factor(SR_env2$Block)

SR_sp2[is.na(SR_sp2)]<-0  #corrected zeros
any(is.na(SR_sp2))

H<-diversity(SR_sp2)
S <- specnumber(SR_sp2)
J <- H/log(S)

#NAs when 1 species,corrected from NA to 1
c<-which(is.na(J))
S[c]

J<-replace_na(J,1)
DiversityDataTmp<-as.data.frame(cbind(H,S,J))
DiversityData<-cbind(SR_env2,DiversityDataTmp)
str(DiversityData)

DivMod<-lmer(J~Site*Treatment+(1|Block/Seeding),data=DiversityData)
plot(DivMod)
anova(DivMod)
pairs(emmeans(DivMod,~Treatment|Site))
```

#Budget
```{r money modeling}
YieldData6<-YieldData5
YieldData6<-YieldData6 %>% 
  mutate(SeedingMetric=Seeding*1000*2.47,
         NitCostMetric=as.numeric(as.character(NitrogenMetric))*20.35610978,
         SeedCostMetric=SeedingMetric*0.000321429,
         IncomeMetric=SeedWeight_kgha*0.685837984,
         Profit_dollarsha=IncomeMetric-(SeedCostMetric))

YieldData6$SeedingMetric<-as.numeric(as.character(YieldData6$SeedingMetric))

ProfitRed<-nlme(Profit_dollarsha~-a*SeedingMetric^2+b*SeedingMetric,
     data=YieldData6,
     start=c(9.813e-07,1.080e-01),
     fixed= list(a~1,b ~ 1),
     random = list(Site=pdDiag(list(a~1,b ~ 1)),
                   Block=pdDiag(list(a~1,b ~ 1))),
     na.action = na.omit)

#Site
ProfitSite<-nlme(Profit_dollarsha~-a*SeedingMetric^2+b*SeedingMetric,
     data=YieldData6,
     start=c(9.813e-07,9.813e-07,1.080e-01,1.080e-01),
     fixed= list(a~Site,b ~ Site),
     random = list(Site=pdDiag(list(a~Site,b ~ Site)),
                   Block=pdDiag(list(a~Site,b ~ Site))),
     na.action = na.omit)

anova(ProfitRed,ProfitSite)
#Nitrogen
ProfitNitrogen<-nlme(Profit_dollarsha~-a*SeedingMetric^2+b*SeedingMetric,
     data=YieldData6,
     start=c(9.813e-07,9.813e-07,9.813e-07,1.080e-01,1.080e-01,1.080e-01),
     fixed= list(a~Nitrogen,b ~ Nitrogen),
     random = list(Nitrogen=pdDiag(list(a~Nitrogen,b ~ Nitrogen)),
                   Block=pdDiag(list(a~Nitrogen,b ~ Nitrogen))),
     na.action = na.omit)
anova(ProfitRed,ProfitNitrogen)

fixef(ProfitRed)
fixef(ProfitSite)
fixef(ProfitNitrogen)

#profit ploy
fun.1Profit <- function(x) -fixef(ProfitRed)[1]*x^2+fixef(ProfitRed)[2]*x  
optimize(fun.1Profit, interval=c(0,741300),maximum = T)

#tiff("Fig5.tiff", units="in", width=5.82, height=5.54, res=300)
ggplot(YieldData6,aes(x=SeedingMetric,y=Profit_dollarsha))+
  geom_point()+
  stat_function(fun=fun.1Profit,size=1.2)+
  geom_segment(aes(x = 527800.3, y = 0, xend = 527800.3, yend = 2237.864),
               size=.3,arrow = arrow(length = unit(0.3, "cm"),type = "closed"))+
  scale_y_continuous(expand = c(0, 0),labels = scales::comma,limits=c(0,4000)) +
  scale_x_continuous(labels = scales::comma,
                     breaks=c(0,185300,370700,556000,741300))+
  scale_color_brewer(palette = "Accent")+
  theme_bw(base_size = 18)+
   labs(y=expression("Partial returns (dollars"~ha^-1*')'),
       x=expression("Seeding rate (seeds"~ha^-1*')'))+
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(hjust=1),
        legend.position="none")
#dev.off()
#################
```